Tempo and mode of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2020-07-01 manuscript.tex
Small update to latter part of intro

Main et al. \citep{Main:2013dg}, used a separate TSS profiling method in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa: \textit{D. simulans}, \textit{D. pseudoobscura} and \textit{D. sechellia}. The authors found that the location and estimated activities of orthologous TSSs to be generally conserved, but did observe instances of TSS variation that suggest new promoters. Notably, \textit{Main et. al.} found differences in promoter selection in the Alcohol dehydrogenase (ADH) gene across the four species. Working with high-resolution promoter data in human and mouse, Young and colleagues \citep{Young:2015xx} found that more than half (56\$) of promoters were turned over between the two species. #continue here

>>>>

Main et al. \citep{Main:2013dg}, used a separate TSS profiling method in \textit{D. melanogaster} to identify putative orthologous TSSs in three other \textit{Drosophila} taxa: \textit{D. simulans}, \textit{D. pseudoobscura} and \textit{D. sechellia}. The authors found that the location and estimated activities of orthologous TSSs to be generally conserved, but did observe instances of TSS variation that suggest new promoters. Notably, \textit{Main et. al.} found differences in promoter selection in the Alcohol dehydrogenase (ADH) gene across the four species. Working with high-resolution promoter data in human and mouse, Young and colleagues \citep{Young:2015xx} found that more than half (56\$) of tissue-matched promoters were turned over between the two species. From and measurements of selective constraint the concluded that promoter turnover is the major source of promoter gain and loss in mammals. xxxx fix that sentence
